Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-27 Final_Manuscript.Rmd
added references

##Self-Objectification
Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008]. @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait. Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@calogero2011, @moradi2008]. Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification]. Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?

@@

##Interpersonal Objectification
SIMO model and literature review [@gervais2020social]. Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@young1979]. Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998]. We don't know about women-on-women interpersonal objectification. What might be different?

>>>>

##Self-Objectification
Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level [@loughnan2015exploring] to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level [@calogero2011; @moradi2008]. @calogero2011 proposes that the construct of self-objectification can be conceptualized as a learned trait. Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines, which can lead to a state of self-objectification [@bernard2018bodies; @calogero2011; @moradi2008]. Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) [@fredrickson1998swimsuit, @garcia2016objectification]. Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?

@@

##Interpersonal Objectification
SIMO model and literature review [@gervais2020social]. Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979]. Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998]. We don't know about women-on-women interpersonal objectification. What might be different?
